Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-02-24 Manuscript_TIFS/manuscript_TIFS.tex
Threat Model grammar update

\section{Introduction}
\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are acquired by the application developers from users, such as the shopping app users' purchase record data, patients' clinical data and etc. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from users anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning (FL) \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}. Bonawitz \textit{et al.} built the first FL system which is operated on Google's mobile phone to train a global model based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. Furthermore, some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.

@@

\par Since thousands of clients from different sources may participate in the training process, security issues also exist in the distributed FL system. On one hand, former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}. On the other hand, FL faces threats from the poisoning attacks launched by malicious attackers among the FL clients \cite{miao2018attack, laishram2016curie}. And such attacks are referred to as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}. By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the global model to learn incorrect knowledge. As a result, this process renders the central server's global model obsolete. Furthermore, Byzantine attacks can be separated into two types according to the attack consequences. In the first type of Byzantine attacks, called denial-of-service attack (including untargeted attacks, targeted attacks, e.g), the Byzantine attackers intend to disturb the global model thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. In another type of Byzantine attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples which have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the development of a Byzantine-robust aggregation algorithm that distinguishes suspected clients from benign clients. The suspected clients' gradient updates are subsequently removed from the aggregation process by the server. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine clients without excluding Byzantine clients like Median \cite{ref_16_defense}. In Median, The FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates. In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL, based on the preceding research. Our contributions are four-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called EFL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is flexible for it is compatible with different deep learning models in different clients.
  \item We craft a `phishing' method based on EFL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the EFL architecture, which preserves the security of EFL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
\end{itemize}

@@

\par \textit{1) Denial-of-Service Byzantine Attack:} In denial-of-service attack, the Byzantine attackers intend to disturb the global model thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. The label flipping attack in the current system model can be used by a malicious Byzantine client $b_i$ to launch Byzantine attacks against the global model. Label flipping attacks require $b_i$ to change the labels of training data while ensuring that the data's features remain unchanged \cite{ref_18_label_flipping}. The local model of the Byzantine client $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy. Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server. Therefore the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients. The server $s$'s aggregation process is performed on FedAvg which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to enlarge the impact of attack. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions. 
\par In section V, we first divided denial-of-service attacks into 2 types of attacks: The first one is untargeted attack which makes the Byzantine attackers change the label of data samples from a type into another type (for instance, all the samples with label `5' are changed to label `0'). The another one is random attack which makes the Byzantine attackers randomly change the label of data samples. Then we evaluated our framework against the 2 types of denial-of-service attacks.
\par \textit{2) Backdoor Byzantine Attack:} In backdoor attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples which have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}. Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset. Then they relabel the data samples with $\sigma$ as the target label $\iota$. Each backdoor attacker adopts the preprocessed local dataset with $\sigma$ to update the global model it received from the FL server. Then it transfers the poisoned model updates which contain the information that the data sample with $\sigma$ is predicted as the target label $\iota$ to the FL server. After receiving the poisoned model updates, the FL server updates the global model using the poisoned model updates of the backdoor attackers. After the update, the FL server's model misclassifies the data with the $\sigma$ to the target label $\iota$ of backdoor attackers. Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example. The backdoor attacker adds a grey square as $\sigma$ in each data sample. Each data sample with a $\sigma$ is labeled as `cat'. Then the backdoor attacker uses these data samples to update the global model from the central server and transfers the model gradient updates containing the $\sigma$ information to the central server. After that, the central server updates the global model via the model gradient updates. Thus, the global model learns the $\sigma$ information from the backdoor attacker. It misclassifies the data sample with the $\sigma$ as 'cat' as well.
\par In section IV.D, we did theoretical analysis about how our FLPhish scheme can defend against backdoor Byzantine attacks.

>>>>

\section{Introduction}
\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are acquired by the application developers from users, such as the shopping app users' purchase record data, patients' clinical data, and etc. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from users anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning (FL) \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}. Bonawitz \textit{et al.} built the first FL system that is operated on Google's mobile phone to train a global model based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team from WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. Furthermore, some former researchers have also applied FL to some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.

@@

\par Since thousands of clients from different sources may participate in the training process, security issues also exist in the distributed FL system. On one hand, former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}. On the other hand, FL faces threats from the poisoning attacks launched by malicious attackers among the FL clients \cite{miao2018attack, laishram2016curie}. And such attacks are referred to as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}. By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the global model to learn incorrect knowledge. As a result, this process renders the central server's global model obsolete. Furthermore, Byzantine attacks can be separated into two types according to the attack consequences. In the first type of Byzantine attacks, called denial-of-service attacks (including untargeted attacks, targeted attacks, e.g), the Byzantine attackers intend to disturb the global model thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. In another type of Byzantine attack, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples that have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the development of a Byzantine-robust aggregation algorithm that distinguishes suspected clients from benign clients. The suspected clients' gradient updates are subsequently removed from the aggregation process by the server. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine clients without excluding Byzantine clients like Median \cite{ref_16_defense}. In Median, the FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates. In this study, we provide a unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in EFL. Our contributions are three-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called EFL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is flexible because it is compatible with different deep learning models on different clients.
  \item We craft a `phishing' method based on EFL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the EFL architecture, which preserves the security of the EFL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
\end{itemize}

@@

\par \textit{1) Denial-of-Service Byzantine Attack:} In denial-of-service attacks, the Byzantine attackers intend to disturb the global model, thus making it produce wrong predictions of the normal dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. The label flipping attack in the current system model can be used by a malicious Byzantine client $b_i$ to launch Byzantine attacks against the global model. Label flipping attacks require $b_i$ to change the labels of training data while ensuring that the data's features remain unchanged \cite{ref_18_label_flipping}. The local model of the Byzantine client, $b_i$ is trained with incorrect labels, resulting in a `poisoned' model with low accuracy. Then Byzantine client $b_{i}$ dispatches the false model gradient updates to the central server. Therefore, the false model gradient updates cause the central server to learn the falsely distilled knowledge from clients. The server $s$'s aggregation process is performed on FedAvg, which takes each client $c_{i}$'s dataset $d_{i}$'s size as the aggregation weight for $c_{i}$. This means that a client $c_{i}$ with a larger size of $d_{i}$ gets a larger aggregation weight. Meanwhile, FedAvg takes the size of $d_{i}$ declared by $c_{i}$ as $d_{i}$'s real size, which means $b_{i}$ can declare a fake size value larger than $d_{i}$'s real size value to increase the impact of the attack. If the weight of the malicious clients reaches a threshold, the central server is misguided to produce false predictions. 
\par In section V, we first divided denial-of-service attacks into 2 types of attacks: The first one is the untargeted attack, which makes the Byzantine attackers change the labels of data samples from one type into another type (for instance, all the samples with label `5' are changed to label `0'). Another one is the random attack which makes the Byzantine attackers randomly change the label of data samples. Then we evaluated our framework against the 2 types of denial-of-service attacks.
\par \textit{2) Backdoor Byzantine Attack:} In backdoor attacks, called backdoor attacks, the disturbed global model will make wrong predictions of the data samples that have `backdoor' in them \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}. Backdoor attackers in FL need to embed some `triggers' (noted as $\sigma$) in their local dataset. Then they relabel the data samples with $\sigma$ as the target label $\iota$. Each backdoor attacker adopts the preprocessed local dataset with $\sigma$ to update the global model it received from the FL server. Then it transfers the poisoned model updates, which contain the information that the data sample with $\sigma$ is predicted as the target label $\iota$ to the FL server. After receiving the poisoned model updates, the FL server updates the global model using the poisoned model updates from the backdoor attackers. After the update, the FL server's model misclassifies the data with the $\sigma$ to the target label $\iota$ of backdoor attackers. Take a backdoor attack process towards the construction of an FL on CIFAR-10 as an example. The backdoor attacker adds a grey square as $\sigma$ in each data sample. Each data sample with a $\sigma$ is labeled as `cat'. Then the backdoor attacker uses these data samples to update the global model from the central server and transfers the model gradient updates containing the $\sigma$ information to the central server. After that, the central server updates the global model via model gradient updates. Thus, the global model learns the $\sigma$ information from the backdoor attacker. It misclassifies the data sample with the $\sigma$ as 'cat' as well.
\par In section IV.D, we did a theoretical analysis of how our FLPhish scheme can defend against backdoor Byzantine attacks.
